\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{nopageno}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage[dvipsnames]{xcolor}
\geometry{
  letterpaper,
  top=0.75in,
  left=0.75in,
  bottom=1in,
  right=0.75in,
  left=1in}
\definecolor{blue(ryb)}{rgb}{0.1, 0.4, 0.8}
\newcommand{\hdr}[1]{\textcolor{blue(ryb)}{\textbf{#1}}}
\newcommand{\role}[3]{\underline{\textbf{#1}, {#2}} \hfill #3}
\renewcommand{\labelitemi}{\labelitemii}

\begin{document}
\begin{center}
\hdr{\Large{Hannah Friedman}}\\
\end{center}
Email: hannahfriedman@berkeley.edu \hfill Department of Mathematics\\
Website: \url{hannahyfriedman.com} \hfill University of California, Berkeley

\bigskip
\raggedright
\hdr{EDUCATION}\\
\textbf{\underline{University of California, Berkeley}} \hfill Expected May 2026\\
PhD Candidate in Mathematics jointly advised by Bernd Sturmfels and Serkan Ho\c{s}ten\\
\textbf{\underline{Harvey Mudd College}} \hfill May 2023\\
BS in Mathematics with High Distinction, Honors in Mathematics\\
Thesis advised by Michael Orrison

\bigskip

\hdr{AWARDS \& HONORS}\\
\role{Chancellor's Fellowship}{UC Berkeley}{2023}\\
\role{Alvin White Prize}{Harvey Mudd College}{2023}\\
\textit{Presented to a student or students who have contributed greatly to the humanistic side of the Harvey Mudd College Mathematics Community.}\\
\role{Giovanni Borrelli Mathematics Fellowship}{Harvey Mudd College}{2021 - 2022}\\
\textit{Conferred on one or two junior mathematics majors in recognition of the ability to complete high quality research independently or in tandem with a faculty advisor.}\\
\role{Courtney S. Coleman Prize}{Harvey Mudd College}{2021}\\
\textit{Awarded to three rising juniors who excel in mathematics.}

\bigskip

\hdr{RESEARCH ACTIVITES}\\
\begin{itemize}
\item Visit to Max Planck Institute for Mathematics in the Sciences \hfill Leipzig, Summers 2023-2025  
  \item SL Math Summer School: New Perspectives on Discriminants and Applications \hfill MPI MiS, June 2025
  \item Problem-Solving Workshop: Computational Geometric Analysis \hfill CUNY Graduate Center, May 2025
  \item Workshop on the Applications of Commutative Algebra \hfill The Fields Institute, May 2025
  \item Organized Non-Linear Algebra Seminar \hfill UC Berkeley, December 2024
  \item Workshop for Women in Algebraic Statistics \hfill St John's College, Oxford, July 2024
\end{itemize}

\bigskip

\hdr{PUBLICATIONS}\\
\begin{itemize}
\item Renato G. Bettiol, Hannah Friedman.
  Counting Homogeneous Einstein Metrics.
  Submitted (2025).
\item Paul Breiding, Taylor Brysiewicz, Hannah Friedman.
  Homotopy Iterators.
  Submitted (2025). 
\item Hannah Friedman, Bernd Sturmfels, Max Wiesmann.
  Squared Linear Models.
  \textit{SIAM Journal on Applied Algebra and Geometry} (2025+). 
\item Hannah Friedman, Serkan Ho\c{s}ten.
  Grassmann and Flag Varieties in Linear Algebra, Optimization, and Statistics: An Algebraic Perspective.
  Submitted (2025).
\item Yulia Alexandr, Kristen Dawson, Hannah Friedman, Fatemeh Mohammadi, Pardis Semnani, Teresa Yu.
  Decomposing Conditional Independence Ideals with Hidden Variables. Submitted (2025).
\item Hannah Friedman.
  Likelihood Geometry of the Squared Grassmannian. \textit{Proceedings of the American Mathematical Society}, \textbf{153} (2025) 4463-4474.
  \item Karel Devriendt, Hannah Friedman, Bernhard Reinke, Bernd Sturmfels.
    The Two Lives of the Grassmannian.
    \textit{Acta Universitatis Spientiae, Mathematica}, \textbf{17} (2025) 8. 
\item Hannah Friedman, Bernd Sturmfels, Max Zubkov.
  Likelihood Geometry of Determinantal Point Processes.
  \emph{Algebraic Statistics}, \textbf{15} (2024) 15-25.
\item Hannah Friedman. Long Increasing Subsequences, senior thesis advised by Michael Orrison. 
\item Hannah Friedman, Amani R. Maina-Kilaas, Julianna Schalkwyk, Hina Ahmed, and Jamie Haddock. 
  An Interpretable Joint Nonnegative Matrix Factorization-Based Point Cloud Distance Measure, \emph{Proceedings of the Conference on Information Sciences and Systems (CISS)}, Baltimore, MD, March 2023.
\end{itemize}

\bigskip

\hdr{TALKS}\\
Key: $\clubsuit$ = invited; $\spadesuit$ = contributed; $\diamondsuit$ = seminar/lecture.
\begin{itemize}
\item Counting Homogeneous Einstein Metrics.\\
  $\clubsuit$ Santa Clara University Mathematics and Computer Science Colloquium, November 11, 2025. \\
  $\clubsuit$ San Francisco State University Algebra, Combinatorics, and Geometry Seminar, October 8, 2025.\\
  $\diamondsuit$ UC Berkeley Seminar on Commutative Algebra and Algebraic Geometry, September 30, 2025. \\
\item Grassmann and Flag Varieties in Linear Algebra, Optimization, and Statistics: An Algebraic Perspective.\\
  $\clubsuit$ New Frontiers of Geometry and Combinatorics in Machine Learning at SIAM AG, July 10, 2025.
\item Squared Linear Models\\
  $\diamondsuit$ MPI MiS Seminar on Nonlinear Algebra, June 19, 2025.
\item Solving Polynomial Equations (Software Demsonstration)\\
  $\clubsuit$  Problem Solving Workshop: Computational Geometric Analysis, June 4, 2025.
\item Likelihood Geometry of the Squared Grassmannian\\
  $\clubsuit$ Session on Advances in Applied Algebra and Algebraic Statistics at the AWM Resarch Symposium, March 27, 2025.\\    
  $\spadesuit$ AlgStat 2025, March 27, 2025.\\  
  $\clubsuit$ AMS Special Session on Algebraic Statistics in Our Changing World at JMM, January 8, 2025.\\
  $\diamondsuit$ UC Berkeley Combinatorics Seminar, October, 2024.\\
  $\spadesuit$ Workshop for Women in Algebraic Statistics at St. John's College, Oxford, July, 2024.
\item Likelihood Geometry of the Squared Grassmannian\\
  $\diamondsuit$ University of Wisconsin Applied Algebra Seminar, May 15, 2025.
\item The Squared Grassmannian\\
  $\clubsuit$ University of Washington Combinatorics and Geometry Seminar, January 15, 2025.
\item What is algebraic statistics?\\
  $\spadesuit$ Bay Area Discrete Math Day, December 7, 2024. 
\item Optimization over Two Embeddings of the Grassmannian\\
  $\clubsuit$ Codex seminar, July 2024. 
\item Likelihood Geometry of Determinantal Point Processes\\
  $\diamondsuit$ Algebra-Geometry-Combinatorics Afternoon at SFSU, November 2023.
\item Long Increasing Subsequences\\
  $\spadesuit$ Harvey Mudd Thesis Presentation Days.
\item A New Basis for $k$-Local Class Functions\\
  $\spadesuit$ 2023 Joint Math Meetings.
\end{itemize}

\bigskip


\hdr{TEACHING \& MENTORSHIP}\\
\begin{itemize}
\item Unbounded Representation Leader, Fall 2024 - current
\item Graduate Student Instructor at UC Berkeley:
  \begin{itemize}
  \item Math 16B: Analytic Geometry and Calculus, Fall 2025
  \item Math 250B: Graduate Commutative Algebra, Spring 2025
  \item Math H110: Honors Abstract Linear Algebra, Spring 2025
  \item Math 55: Discrete Math, Fall 2024
  \item Math 1A: Calculus I, Spring 2024
  \end{itemize}
\item UC Berkeley Directed Reading Program Mentor, Spring 2024 \& Fall 2025
\item President of Women in Math at Harvey Mudd College, Fall 2022-Spring 2023
\end{itemize}

\bigskip

\hdr{SKILLS}\\
\begin{itemize}
\item 
Programming Languages: Python, MatLab, Macaulay2, Java, C++, R, Julia\\
\item 
Languages: English (fluent), German (fluent), Mandarin (proficient), Hebrew (proficient)
\end{itemize}
\end{document}
